---
title: "SESYNC MPA and Climate Change DBEM Analysis"
author: ""
date: "04/05/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# 1.Overall approach

## 1.1 Step 1 (Ecology)

We first average the Fish Model's Maximum Catch Potential (MCP) of 1995 to 2014 (last years of fisheries data from SAU) for each species for each one of the circulation models (GCM) that we work with (GFDL, MPIL, IPSL). Secondly, we average the 2005-2014 average for all models (To get the 10 years average; "today"). Thirdly, we repeat the steps using the abundance data.

**Result of step 1:** The result is the mean MCP of all models and time period for each species in our database for each grid-cell of the world.

## 1.2 Step 2 (Economics)

We estimate fisheries revenues as the weighted average price multiplied by the predicted catch in each cell. As countries have different prices for different species, we used current catch proportions by country and species in each cell to derive a weighted average price per tonne for each species. The weighted price was established using the proportion of each country’s catch multiplied by the country-species specific price. All prices were drawn from a global fisheries ex-vessel price database (Tai et al. 2017). We assume a discount rate of 4%. We calculated the existence value as the potential ex-vessel value of the species (their current ex-vessel price multiplied by their biomass). Within a no-take MPA, catches are assumed to be zero. If a cell is partially occupied by a no-take MPA, the fishing mortality (and thus catches) of a species is reduced by the proportion of the cell area occupied by the MPA.

**Result of step 2:** The result is the mean fisheries revenue of all models and time period for each species in our database for each grid-cell of the world. We also compute the existence value calculated as the mean weighted fish price multiplied by ABD for each species for each cell. 

## 1.3 Step 3 (Final Result)

**Result of step 3:** We want MCP,ABD and economic value, per grid cell Today (1995 - 2014); Mid century (2041-2060); End Century (2080-2099).

# 2. Pre-Analysis; Determine MPA percentage grid

```{r setup, eval=T, echo=F, warning=F,message=F, results = 'hide'}

#### READ ME !!! ####
# This chunk runs all the pkgs needed for the analysis
# Run this chunk before knit so you make sure you have all pkgs installed in R
# If you want to run it you will need to change the "path" of the DBEM_imp_F.R function

#### Set up packages ####

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}


#### Library ###
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggpubr", #Nice grpahs and spatial analysis
  "gridExtra", # For gridarrange
  "cowplot", # For putting graphs in nice grids
  "knitr",
  "data.table",
  "stringr", # for string analysis
  "rgdal", # Spatial analysis 
  "tools", # Spatial analysis 
  "sf", # Shapefile packages
  "broom", # for multiple statistics
  "moments", # for exploring normallity
  "rfishbase", # for getting spp hab
  "wesanderson"
  )

ipak(packages)

# Functions needed to run the analysis
source("./Functions/species_function.R")
source("./Functions/rcp_summary.R")
source("./Functions/DBEM_imp.R")
source("./Functions/model_results.R")

```


```{r Grid_Analysis, eval=F, echo=T}

# Create dataset of MPAs to incorporate into the DBEM
# NOTE:
# grid_MPA_notake.csv <- was created using ARCGIS (SA) using the World Data base


# Data
grid_MPA_notake <- read.csv("/nfs/mpasandclimatechange-data/Data/MPA/grid_MPA_notake.csv")
# View(grid_MPA_notake)

# Formula in the DBEM
# x *(1-MPA_Index(i))

# Double check it make sense

FM = rnorm(259200,0.5,.1)

Check_Data <- grid_MPA_notake %>% 
  mutate(
    FM = FM,
    NoTakeProp = NoTakePercent/100,
    Test = round(FM * (1-NoTakeProp),2)
  ) %>% 
  filter(NoTakeProp > 0)

ggplot(Check_Data) +
  geom_tile(
    aes(
      x = Lon,
      y = Lat,
      colour = NoTakeProp,
      fill =NoTakeProp
    )
  ) +
  geom_sf(data = World_Land_sf,
          aes()
  ) + scale_colour_gradient2() +
  scale_fill_gradient2()


# Yes, makes sense! 

#  Creating datafile for DBEM (Computecanada)
MPA_Indexb <- grid_MPA_notake %>% 
  mutate(NoTakeProp = NoTakePercent/100) %>% 
  select(NoTakeProp)

write.csv(MPA_Indexb,
          "MPA_Indexb.txt",
          row.names = F
          )
```


# 3. Run Analysis

## Run SESYNC model on DBEM data

```{r Control_pannel, eval=T, echo=F}

# Load all data needed to run the routine

# Time frame
year_df <- tibble(year =  c(seq(1995,2014,1), seq(2041,2060,1), seq(2081,2100,1)),
                  time_period = c(rep("Today", 20), rep("Mid Century", 20), rep("End of Century", 20))
                  )


#Get list of species for analysis by comparing between MPA and Fish model species lists:
mpa_model_species <- data_frame(x = list.files("/nfs/mpasandclimatechange-data/Data/DBEM/MPA_Model/GFDL26"))
fish_model_species <- data_frame(x = list.files("/nfs/mpasandclimatechange-data/Data/DBEM/Fish_Model/GFDL26"))
exploited_species <- inner_join(mpa_model_species, fish_model_species)

# Spatialzied catch data (From SAU) (Pauly & Zeller, 2015)
country_species_catch_prop <- fread("/nfs/mpasandclimatechange-data/Data/Economics/CountrySpeciesCatchProp.csv")

# Price data (From FERU) (Tai et al., 2017, Sumaila et al. 2005)
prices <- fread("/nfs/mpasandclimatechange-data/Data/Economics/FERU_Price_Averaged.csv")

# Estimate who catches what for estimating price
country_prop_price <- left_join(country_species_catch_prop, prices) %>%
  rename(INDEX= cell_id) %>% 
  mutate(fishing_entity_id = as.character(fishing_entity_id),
         taxon_key = as.character(taxon_key),
         price = as.numeric(as.character(price)),
         price = if_else(is.na(price), 1496, price),
         weighted_price = price * prop,
         weighted_flexibility = flexibility * prop
  ) %>%
  group_by(INDEX, taxon_key) %>% 
  summarize(price = sum(weighted_price),
            flexibility = sum(weighted_flexibility)
  ) %>% 
  ungroup() 

# Load Lat long data of the world
Lon_Lat_DBEM <- fread("/nfs/mpasandclimatechange-data/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Lon_Lat_DBEM) <- c("INDEX","Longitude","Latitude")    

```


```{r main_routine, eval = T, echo = F}

# This chunk runs the model for each conservation (fish and MPA) and climate change (low and high) scenario

start <- Sys.time()
fish_26 <- model_results(Model="Fish", 
                         RCP="26",
                         species_list=exploited_species$x, 
                         GCM=NA, 
                         year_df=year_df, 
                         country_prop_price=country_prop_price)
end <- Sys.time()
fish26_time <- as.character(end-start)

start <- Sys.time()
fish_85 <- model_results(Model="Fish", 
                         RCP="85", 
                         species_list=exploited_species$x, 
                         GCM=NA, 
                         year=year_df, 
                         country_prop_price=country_prop_price) 
end <- Sys.time()
fish85_time <- as.character(end-start)
start <- Sys.time()
mpa_26 <- model_results(Model="MPA", 
                        RCP="26", 
                        species_list=exploited_species$x, 
                        GCM=NA, 
                        year=year_df, 
                        country_prop_price=country_prop_price)
end <- Sys.time()
mpa26_time <- as.character(end-start)
start <- Sys.time()
mpa_85 <- model_results(Model="MPA", 
                        RCP="85", 
                        species_list=exploited_species$x, 
                        GCM=NA, 
                        year=year_df, 
                        country_prop_price=country_prop_price) 
end <- Sys.time()
mpa85_time <- end-start

```

# 4. Results

## 4.1 Functions needed to get results

Load functions needed for analyzing results

### 4.1.1 `FUN_ReadResults`

This function simply reads the results in one single data frame

```{r FUN_ReadResults, eval = T, echo = F}

# This function loads the datasets depending on the model and RCP. 


Read_Results <- function(Model,RCP,Path="NA"){
  require(DT)
  require(dplyr)
  
  # If path changes
  if(Path == "NA"){
    File_Path <- "/nfs/mpasandclimatechange-data/Data/Results/"
  }else{
    File_Path <- Path
  }
  
  
  # For both models in once
  if(Model == "Both"){
    
    F_File <- paste("Fish_RCP",RCP,"_All_GCMs_20.csv", # include Wave_ for old results
                    sep="")
    
    M_File <- paste("MPA_RCP",RCP,"_All_GCMs_20.csv", # include Wave_ for old results
                    sep="")
    
    F_Data <- fread(paste(File_Path,F_File,
                          sep=""))
    
    M_Data <- fread(paste(File_Path,M_File,
                          sep=""))
    
    Both_Models <- F_Data %>% 
      bind_rows(M_Data) %>% 
      filter(time_period != "NA")
    
    return(Both_Models)
    
  }else{
    
    File <- paste(Model,"_RCP",RCP,".csv", 
                  sep="")
    
    Data <- fread(paste(File_Path,File,
                        sep=""))
    
    return(Data)
    
  }
  
}
```

### 4.1.2 `FUN_ggthemes`

This function standardizes `ggplot` themes among all plots

```{r FUN_ggtheme, eval =T, echo = F}


# Standarization of plots
ggtheme_Plot <- function() {
  theme(
    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    strip.background = element_blank(),
    # strip.text       = element_text(size = base_size, face = "italic"),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 18,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 18),
    axis.title = element_text(size = 20),
    legend.key = element_rect(colour = NA, fill = NA),
    legend.position  = "top",
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    strip.text.x = element_text(size = 18, colour = "darkgrey"),
    strip.text = element_text(size = 18)
  )
}

# Standarization of maps
ggtheme_Map <- function(base_size = 9, Region = "NA") {
  theme(
    # text             = element_text(#family = "Helvetica",color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width = unit(5,"line"),
    legend.title = element_text(size = 22, colour =),
    legend.text = element_text(size = 20)
  )
}
```

## 4.2 Load Data and Results

```{r Load_Results, eval = T, echo = F}

# Data needed for the analysis

# ---------------- #
# Spatial Data 
# ---------------- #

# Latitude_Long_Data
Lon_Lat_DBEM <- fread("/nfs/mpasandclimatechange-data/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Lon_Lat_DBEM) <- c("INDEX","Longitude","Latitude")   

# World land polyon for maps

# The path
path_world <- "/nfs/mpasandclimatechange-data/Data/Spatial_Data/World_Land"

# File name
file_name <- "TM_WORLD_BORDERS"

#Load it!
World_Land_sf <- st_read(dsn = path_world, 
                         layer = file_path_sans_ext(file_name)
)

# Base plot
World_Map <- ggplot(World_Land_sf) +
  geom_sf()


# MPA shapefiles

path_MPA <- "/nfs/mpasandclimatechange-data/Data/MPA"

# File name
MPA_file_name <- "CM_noTake"

#Load it!
MPA_sf <- st_read(dsn = path_MPA, 
                         layer = file_path_sans_ext(MPA_file_name)
                  ) %>% 
  st_transform(crs = 4326)


# head(MPA_sf)
# ggplot(MPA_sf) +
#   geom_sf()


# MPA touching grid dataset (0= no MPA, 1=MPA, 2=touching)"
MPA_Grid <- fread("/nfs/mpasandclimatechange-data/Data/MPA/grid_MPA_touching.csv",header = TRUE) %>% 
  rename(INDEX = Seq) %>% 
  select(-Lon,-Lat)

# hist(MPA_Grid$Distance)

# ---------------- #
# SESYNC-DBEM Data 
# ---------------- #

# Fish and MPA model for RCP 2.6
Both_Models26 <- Read_Results("Both","26") %>% 
  mutate(RCP = as.character(RCP))

# Fish and MPA model for RCP 8.5
Both_Models85 <- Read_Results("Both","85") %>% 
  mutate(RCP = as.character(RCP))

# Join both models in one dataset for plotting

### First, filter out regions where data is allways 0 (A.k.A we have no species there)
NoData <- Both_Models85  %>% 
  bind_rows(Both_Models26) %>% 
  group_by(INDEX) %>% 
  summarise(sum= sum(total)) %>% 
  filter(sum == 0) %>% 
  pull(INDEX)

#### Then, join models and filter out those regions where no spp. were evaluated
All_Models <- Both_Models85  %>% 
  bind_rows(Both_Models26) %>% 
  # This is needed to remove cells that are ceros but actually have no fish data
  filter(!INDEX %in% NoData) %>% 
  select(-n)
  

# Path for saving results (Note that we have ./Figures for figures)
Result_Path <- "./data/Data/Results"


```


# 5. Paper Figures

## Fig. 1 -Delta time just for MPA

Figure 1. Change in biomass under climate change, incorporating current no-take MPAs.** Results for mid century (2041-2060) relative to present (1995-2014) under a high emission scenario (RCP 8.5). Results from the MPA model with MPAs included in this study outlined in black.

```{r Fig_one__Data, eval = T, echo = F}

Delta_Time <- All_Models %>% 
  spread(time_period,total) %>% 
  mutate_at(vars(`Mid Century`, # Estimate percentage differences
                 `End of Century`),
            funs(ifelse(Today == 0 & . == 0, 0, # If for no change than 0
                        ifelse(Today == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               ((.-Today)/((.+Today)/2))*100 # Estimate percentage differences
                        )
            )
            )
  ) %>% 
  gather("time_period","MCP_Chng",`Mid Century`,`End of Century`) %>% 
  select(-Today) %>%
  mutate(
    MCP_Chng = ifelse(is.na(MCP_Chng), 0, MCP_Chng), 
    Per = ifelse(MCP_Chng <= -25, -25,
                 ifelse(MCP_Chng >= 25, 25,MCP_Chng) # Just to set the percentage bounds
    )
  ) %>% 
  filter(Measure == "Mean") %>% 
  left_join(MPA_Grid,
            by = "INDEX")


# head(Delta_Time)
# max(Delta_Time$Per)
# min(Delta_Time$Per)

```


```{r Figure_One_plot, eval = T, echo = F}

ggplot() +
  geom_tile(data = subset(Delta_Time, 
                          Model == "MPA" &
                            Data_Type == "Abd" &
                            time_period == "Mid Century",
                          RCP = 85),
              aes(
                x = Longitude,
                y = Latitude,
                fill = Per
              )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  geom_sf(data = MPA_sf, colour = "black", fill = NA, size = 0.5) +
  scale_fill_gradient2("Percentage Change in Biomass (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
                       ) +
  ggtheme_Map() +
  guides(fill = guide_legend(title.position = "top",
                             label.position = "bottom",
                             title.hjust = 0.5,
                             nrow = 1,
                             byrow = TRUE)
  ) +
  ggsave(
    width = 12,
    height = 7,
    units = "in",
    filename = "Figure1.png",
    path= "./data/Global Paper/Submission/Figures"
  )


```

## Fig. 2. Boxplot changes over time MPA

Fig. 2. Percentage change of biomass within regions containing MPAs and in surrounding waters relative to today.** Whiskers represent 1.5* interquartile range. Box represents interquartile range as distance between first and third quartiles. Line represents median, and black points represent outliers (outside of 1.5*IQR)

```{r Fig_two_data, eval = F, echo = T}

Delta_Time_MPA <- All_Models %>% 
  filter(
    Measure == "Mean",
    Model == "MPA",
    Data_Type %in% c("Abd"),
  ) %>% 
  spread(time_period,total) %>% 
  mutate_at(vars(`Mid Century`, # Estimate percentage difference
                 `End of Century`),
            funs(ifelse(Today == 0 & . == 0, 0, # If for no difference than 0
                        ifelse(Today == 0 & . > 0, 100, # If changes from 0 to anything then 100
                               ((.-Today)/((.+Today)/2))*100 # Estimate percentage difference
                        )
            )
            )
  ) %>% 
  gather("time_period","MCP_Chng",`Mid Century`,`End of Century`) %>% 
  select(-Today) %>% 
  left_join(MPA_Grid,
            by = "INDEX") %>% 
  mutate(Per = ifelse(MCP_Chng <= -25, -25,
                      ifelse(MCP_Chng >= 25, 25,MCP_Chng) # Just to set the percentage bounds
  ),
  Touching = ifelse(Touching==1, "MPA",
                    ifelse(Touching==2, "Surrounding",
                           NA
                    )
  ),
  RCP = ifelse(RCP== 26,"Low","High"),
  time_period = ifelse(time_period== "End of Century","B","A"),
  Order = ifelse(RCP == "Low",1,2)
  ) %>% 
  filter(!is.na(Touching))

```

```{r Fig_two_plot, eval = T, echo = F}

ggplot(Delta_Time_MPA,
       aes(
         x = reorder(RCP,Order),
         y = Per,
         fill = Touching
       )
) +
  geom_boxplot() +
  scale_color_manual("Region", 
                     values = wes_palette("Darjeeling2")
  ) +
  scale_fill_manual("Region", 
                    values = wes_palette("Darjeeling2"),
  ) +
  scale_y_continuous("Percentage Change\n(Relative to Today)",
                     labels = c("<-25",seq(-20,20,5),">25"),
                     breaks = c(seq(-25,25,5))) +
  labs(x = "Emission Scenario") + 
  ggtheme_Plot() +
  theme(legend.position = "right",
        strip.background = element_blank(),
        strip.text.x = element_text(size = 18, colour = "black", face = "bold")
  ) +
  facet_wrap(~ time_period,
             labeller=as_labeller(c(
               "B" = "End of Century",
               "A" = "Mid Century"))
  ) +
  ggsave(
    width = 13,
    height = 10,
    units = "in",
    filename = "Figure2.png",
    path= "./data/Global Paper/Submission/Figures"
  )


# Exploring outliers for disucssion
# As expected, most of them are > 40 and <-40

# head(Delta_Time_MPA)
# 
# Lat_mean_Out <- Delta_Time_MPA %>% 
#   filter(Per > 20)
# 
#   ggplot() +
#   geom_raster(data = subset(Lat_mean_Out, Model == "MPA" & Data_Type == "Abundance" & time_period == "Mid Century"),
#               aes(
#                 x = Longitude,
#                 y = Latitude,
#                 fill = Per
#               )
#   )


```


## Fig. 3. - Differences Map

Fig. 3.  Biomass (A) and revenue (B) differences between the MPA and the no-MPA scenarios.** Results for mid century (2041-2060) under high emission scenario (RCP 8.5) within MPA and surrounding cells up to 7.5 decimal degrees (~825 km) from an MPA border representing 99% of the cumulative distribution. Density plots (C) represent the average difference between the MPA and no-MPA models aggregated by latitude (frequency of values from <-25% to >25%) in all areas, waters containing MPAs, surrounding waters, and unprotected water.


```{r Figure_three_Data, eval = T, echo = F}

# ---------------------- #
# Delta Models data (Map)
# ---------------------- #

Results_Data <- All_Models %>% 
  filter(Data_Type %in% c("Abd","revenue"),
         Measure == "Mean",
         RCP == 85
  ) %>% 
  spread("Model","total") %>% 
  mutate(
    MPA = ifelse(is.na(MPA), 0, MPA), # I believe there are parts that MPA model does not have?
    Fish = ifelse(is.na(Fish), 0, Fish),
    Diff_Models = ifelse(MPA == 0 & Fish == 0, 0, # If MPA and Fish are cero, then no difference
                         ifelse(MPA == 0 & Fish > 0, -100, # If MPA is cero but Fish >0 then -100 
                                ifelse(MPA > 0 & Fish == 0, 100, # If MPA > 0 but Fish = 0, then +100
                                       ((MPA-Fish)/((MPA+Fish)/2))*100
                                )
                         )
    ),
    # Just to set the percentage bounds
    Per = ifelse(Diff_Models <= -25, -25,
                 ifelse(Diff_Models >= 25, 25,Diff_Models)
    ),
    # For plot labels
    Data_Type = ifelse(Data_Type == "Abd","Biomass","Revenue")
  ) %>% 
  left_join(MPA_Grid,
            by = "INDEX") %>% 
  mutate(
    Touching_b = ifelse(Touching == 0,"Unprotected",
                        ifelse(Touching == 1, "MPA",
                               ifelse(Touching == 2, "Surrounding",
                                      NA
                               )
                        )
    )
  )

# Exploring the dataset
# head(Results_Data)
# unique(Results_Data$Touching)
# unique(Results_Data$time_period)
# unique(Results_Data$MPApresentNoTake)
# hist(Results_Data$Diff_Models)

# unique(Results_Data$Touching)
# unique(Results_Data$Geo_Region)

# Some NA's... 
# Results_Data %>% 
  # filter(is.na(MPA)C)

# Plot them... 

# Results_Data %>% 
#   filter(is.na(MPA)) %>% 
#   ggplot()+
#   geom_tile(
#     aes(
#       x = Longitude,
#       y = Latitude,
#       fill = Per
#     )
#   )

### Revenue increase spillover

# ---------------------- #
# Spillover data (histograms)
# ---------------------- #

Spillover_diff_Lat <- Results_Data %>% 
  group_by(Latitude, time_period, RCP,Measure,Data_Type, Touching_b) %>% 
  summarize(total_value = mean(Diff_Models), #mean percent change
            n_cells = n(),
            rate = total_value/n_cells)

Spillover_diff_Lat$total_value <- Spillover_diff_Lat$total_value %>% 
  replace_na(0)

Spillover_diff_Lat_1 <- Results_Data %>% 
  group_by(Latitude, time_period, RCP,Measure,Data_Type) %>% 
  summarize(total_value = mean(Diff_Models), #mean percent change
            n_cells = n(),
            rate = total_value/n_cells)

Spillover_diff_Lat_1$total_value <- Spillover_diff_Lat_1$total_value %>% 
  replace_na(0)

```

```{r Fig_three_plot, eval = T, echo = F}

# --------------------- #
# Create maps (A and B)
# --------------------- #

# Abundance Map (A)
Map_Abd <- ggplot() +
  geom_raster(data = subset(Results_Data, Data_Type == "Biomass" & time_period == "Mid Century"),
              aes(
                x = Longitude,
                y = Latitude,
                fill = Per
              )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  scale_fill_gradient2("Change relative to present (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
                       ) +
  ggtheme_Map() +
  theme(legend.position = "")
  

# Revenue Map (B)
Map_Rev <- ggplot() +
  geom_tile(data = subset(Results_Data, Data_Type == "Revenue" & time_period == "Mid Century"),
              aes(
                x = Longitude,
                y = Latitude,
                fill = Per
              )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  geom_sf(data = MPA_sf, colour = "grey50", fill = "grey50", size = 0.5) +
  scale_fill_gradient2("Differences between models (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
                       ) +
  ggtheme_Map() +
  guides(fill = guide_legend(title.position = "top",
                             label.position = "bottom",
                             title.hjust = 0.5,
                             nrow = 1,
                             byrow = TRUE)
  )

# Get legend for cowplot
legend_map <- get_legend(Map_Rev)

# Re-plot without legend
Map_Rev <- Map_Rev +
  theme(legend.position = "")

# --------------------- #
# Create histograms (C)
# --------------------- #

# Abundance Histogram (No Latitudinal differentiation- C top)
Hist_Abd <- ggplot() + 
  geom_path(data = subset(Spillover_diff_Lat, Data_Type == "Biomass" & time_period == "Mid Century"), 
            aes(y=Latitude, 
                x=total_value, 
                color=Touching_b),
            size = 1) +
  geom_path(data = subset(Spillover_diff_Lat_1, Data_Type == "Biomass"),
            aes(y=Latitude, 
                x=total_value, 
                color = "Total"),
            size = 1
            ) +
  scale_color_manual(values = wes_palette("Darjeeling2")) +
  scale_x_continuous(breaks = 0) +
  ggtheme_Plot() +
  labs(x = "",
       y = "") +
  theme(
  axis.text.y = element_blank(),
  legend.position = "",
  legend.key.width = unit(2,"line"),
  legend.title = element_text(size = 22),
  legend.text = element_text(size = 20)
  ) +
  geom_vline(xintercept = 0, colour = "black", linetype = "dotted") 

# Revenue Histogram (No Latitudinal differentiation- C bottom)
Hist_Rev <- ggplot() + 
  geom_path(data = subset(Spillover_diff_Lat, Data_Type == "Revenue" & time_period == "Mid Century"), 
            aes(y=Latitude, 
                x=total_value, 
                color=Touching_b),
            size = 1)  +
  geom_path(data = subset(Spillover_diff_Lat_1, Data_Type == "Revenue"),
            aes(y=Latitude, 
                x=total_value, 
                color = "Total"), 
            size = 1) +
  geom_vline(xintercept = 0, colour = "black",linetype = "dotted") +
  scale_color_manual("Spillover effect by latitude",
                     values = wes_palette("Darjeeling2")
  ) +
  scale_x_continuous(breaks = 0) +
  ggtheme_Plot() +
  labs(x = "",
       y = "") +
  theme(
    axis.text.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_text(size = 22),
    legend.text = element_text(size = 20)
  ) +
  guides(color = guide_legend(title.position = "top",
                              label.position = "right",
                              title.hjust = 0.5,
                              nrow = 1,
                              byrow = TRUE)
  )

# Get legend for cowplot
legend_hist <- get_legend(Hist_Rev)

# Re-plot without legend
Hist_Rev <- Hist_Rev +
  theme(legend.position = "")


# --------------- #
# Plot them all
# --------------- #

plot <- ggdraw() +
  # Abundance
  draw_plot(Map_Abd, x = 0, y = 0.6, width = 0.6, height = 0.4) +
  draw_plot(Hist_Abd, x = 0.59, y = 0.59, width = 0.3, height = 0.4) +
  # Revenue
  draw_plot(Map_Rev, x = 0, y = 0.2, width = 0.6, height = 0.4) +
  draw_plot(Hist_Rev, x = 0.57, y = 0.19, width = 0.3, height = 0.4) +
  # Legends
  draw_plot(legend_map, x = 0, y = 0.1, width = 0.59, height = 0.1) +
  draw_plot(legend_hist, x = 0.60, y = 0.1, width = 0.3, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("A", "B", "C"), 
                  size = 30,
                  x = c(0.0, 0.0, 0.56), 
                  y = c(1, 0.6, 1)
  ) +
  # Uncomment for latitudinal version 
  draw_plot_label(label = c("Revenue", "Biomass"),
                  size = 40,
                  x = c(0.91, 0.91),
                  y = c(0.50, 1),
                  angle = 270,
                  colour = "black"
  )

# Path and name for submission
# Save plot 
save_plot("./data/Global Paper/Submission/Figures/Figure3.png",
          plot,
          base_height = 15,
          base_width = 20
          )


```

# 6. Paper Statistics

We are going to determine the statistical significance of changes between the models (fish/mpa) and time frames (present/future) using a t.test or Wilcox test.

## 6.1 Test assumptions

First we tested for normality by estimating the data skewness and kurtosis. Results show that our results are highly skewed with a sharp peak. Hence we carried out a non-parametric tests.

```{r Test_for_normallity, eval = T, echo = F}

Stats_Data <- All_Models %>% 
  spread("Model","total") %>% 
  mutate(INDEX = as.character(INDEX),
         MPA = ifelse(is.na(MPA), 0, MPA),
         Fish = ifelse(is.na(Fish), 0, Fish)
  ) %>% 
  left_join(MPA_Grid,
            by= "INDEX") %>%  # 1 mpa ; 2 touching
  filter(RCP == 85,
         Measure == "Mean",
         ! Data_Type %in% c("flexibility","nonuse_value"),
         !is.na(Touching)
  )

### Data Histogram

# Fish Model (Not-Normall distribution)
Stats_Data %>% 
  ggplot() +
  geom_histogram(
    aes(
     Fish
    ),
    binwidth = 50
  ) +
  facet_wrap(~Touching)


# MPA Model (Not-Normall distribution)
Stats_Data %>% 
  ggplot() +
  geom_histogram(
    aes(
     MPA
    ),
    binwidth = 50
  ) +
  facet_wrap(~Touching)

### Skewness and  Kurtosis
# S = 0, Perfect; 0-0.5 aprox; 0.5-1 moderate skew; > 5 very skewed

# For MPA (Most of them skewed)
Stats_Data %>% 
  filter(time_period == "Mid Century") %>% 
  group_by(time_period,
           Data_Type,
           Touching) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Skew = skewness(.$MPA)
  ) %>% 
  tidy(Skew)


# For Fish (Most of them skewed)
Stats_Data %>% 
  filter(time_period == "Mid Century") %>% 
  group_by(time_period,
           Data_Type,
           Touching) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Skew = skewness(.$Fish)
  ) %>% 
  tidy(Skew)

# K = 3 stndr normal dist; k > 3 sharper peak High K; k < 3 flatter peak low K

# For MPA (All of them leptokurtic)
Stats_Data %>% 
  filter(time_period == "Mid Century") %>% 
  group_by(time_period,
           Data_Type,
           Touching) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Kurt = kurtosis(.$MPA)
  ) %>% 
  tidy(Kurt)


# For Fish (All of them leptokurtic)
Stats_Data %>% 
  filter(time_period == "Mid Century") %>% 
  group_by(time_period,
           Data_Type,
           Touching) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Kurt = kurtosis(.$Fish)
  ) %>% 
  tidy(Kurt)

### Test for Normality (qqnorm)
# Fish Model

qqnorm(Stats_Data$Fish) # Not really normally dist.
# MPA Model
qqnorm(Stats_Data$MPA) # Not really normally dist.

```

## 6.2 Comparisons between time-periods

Wilcox-on test to compare between time periods 

```{r stats_results_time, eval = T, echo = F}

Delta_Time_Stats <- All_Models %>% 
  spread(time_period,total) %>% 
  left_join(MPA_Grid,
            by = "INDEX") %>% 
  mutate(
    Region = ifelse(Touching==2, "Surrounding",
                    ifelse(Touching==1, "MPA",
                           NA)
    )
  ) %>%
  filter(
    !is.na(Region),
    Measure == "Mean",
    Model == "MPA",
    Data_Type %in% c("Abd")
  ) %>% 
  gather("time_period","Abd",`End of Century`:`Mid Century`) %>% 
  group_by(time_period,
           Region,
           RCP
  ) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Wilcox = wilcox.test(.$Today, .$Abd)) %>% 
  tidy(Wilcox) %>% #Tim doesn't like the "Sig" column
  mutate(Sig = ifelse(p.value > 0.05,"No","Yes"))

# head(Delta_Time_Stats)

write.csv(Delta_Time_Stats,
          "/nfs/mpasandclimatechange-data/Global Paper/Paper_Results/Delta_Time_Stats.csv",
          row.names = F)

```

## 6.3 Estimate how far spillover goes

In here we estimated how far from the border of the MPA the spillover was significantly different than when no MPA was placed

```{r spillover_distance, eval = T, echo = F}

Spillover_Stats_Data <- All_Models %>% 
  spread("Model","total") %>% 
  mutate(#INDEX = as.character(INDEX),
    MPA = ifelse(is.na(MPA), 0, MPA), # I believe there are parts that MPA model does not have?
    Fish = ifelse(is.na(Fish), 0, Fish)
  ) %>% 
  left_join(MPA_Grid,
            by= "INDEX") %>%  # 1 mpa ; 2 touching
  filter(RCP == 85,
         Measure == "Mean",
         ! Data_Type %in% c("flexibility","nonuse_value"),
         !is.na(Touching)
  ) %>% 
  mutate(Bins = cut(Distance,breaks = 9)) %>%
  group_by(time_period,
           Data_Type,
           Bins
  ) %>% 
  do(Wilcox = wilcox.test(.$Fish, .$MPA)) %>% 
  tidy(Wilcox) %>% 
  mutate(Sig = ifelse(p.value > 0.05,"No","Yes")) %>% 
  arrange(desc(Sig))
  
# Check if these cells are anywhere outside the "touching cells" (Yes!!!)

Results_Data %>% 
  filter(Distance < 7.5) %>% 
  pull(Touching_b) %>% 
  unique()


### So... what's the Max value change? 
# Per 25 seems to be fine...

# head(Results_Data)

Results_Data %>% 
  filter(Distance < 7.5) %>%  
  ggplot() +
  geom_histogram(
    aes(x = Diff_Models),
    bins = 100
  )+
  facet_wrap(~Data_Type+time_period+Touching_b) 

# Cumulative distribution of data Mid century

CD_Mid <- Results_Data %>% 
  filter(Distance < 7.5,
         Data_Type == "Abundance",
         time_period == "Mid Century",
         Touching_b == "Open")

unique(CD_Mid$Touching_b)

# Most gridcells are between 0 and around 25%
plot(ecdf(CD_Mid$Diff_Models))

```

## 6.4 Comparisons between models

In here we compared the differences in abundance and MCP between the fish and MPA models to see if they perform differently under climate change

```{r stats_results_models, eval = T, echo = F}

Delta_Models <- All_Models %>% 
  spread("Model","total") %>% 
  left_join(MPA_Grid,
            by= "INDEX") %>%  # 1 mpa ; 2 touching
  filter(Measure == "Mean",
         ! Data_Type %in% c("flexibility","nonuse_value"),
         !is.na(Touching),
         RCP == 85
  ) %>% 
  # Note; change the Distance filter to incorporate the non-sig to the discussion
  mutate(Region = ifelse(Touching == 0 & Distance <= 7.5,"Unprotected", # to find non-sig. 
                         ifelse(Touching == 1, "MPA",
                                ifelse(Touching == 2, "Surrounding", NA
                                )
                         )
  )
  ) %>% 
  group_by(time_period,
           Data_Type,
           Region
  ) %>% 
  # Uses broom to estimate sig.dif with wilcox for each group_by
  do(Wilcox = wilcox.test(.$Fish, .$MPA)) %>% 
  tidy(Wilcox) %>% #Tim doesn't like the "Sig" column
  mutate(Sig = ifelse(p.value > 0.05,"No","Yes"))

write.csv(Delta_Models,
          "/nfs/mpasandclimatechange-data/Global Paper/Paper_Results/Stats_Data_models.csv",
          row.names = F)


Delta_Models %>% 
  # gather("Model","total",Fish:MPA) %>% 
  filter(
    time_period == "Mid Century",
    Data_Type == "Abd",
    RCP == 85,
    Measure == "Mean"
  ) %>% 
  ggplot() +
  geom_tile(
    aes(
      x = Longitude,
      y = Latitude,
      fill = MPA
    )
  )

```

## 6.5 Latitudinal relation

```{r latitudinal_spillover, eval = T, echo = T}

# Abundance LM MPA

LM_Data_MPA <- Results_Data %>% 
  mutate(Abs_Latitude = abs(Latitude)) %>% 
  filter(
    Data_Type == "Biomass",
    Measure == "Mean",
    Touching_b == "MPA",
    time_period == "Mid Century",
    RCP == 85,
    Diff_Models != 0)

LM_MPA  <- lm(LM_Data_MPA$Abs_Latitude~LM_Data_MPA$Diff_Models)
summary(LM_MPA)

plot(LM_Data$Abs_Latitude~LM_Data$Diff_Models)


# Abundance LM Touching

LM_Data_Abd <- Results_Data %>% 
  mutate(Abs_Latitude = abs(Latitude)) %>% 
  filter(
    Data_Type == "Biomass",
    Measure == "Mean",
    Touching_b == "Surrounding",
    time_period == "Mid Century",
    RCP == 85,
    Diff_Models != 0)

LM_Abd_T  <- lm(LM_Data_Abd$Abs_Latitude~LM_Data_Abd$Diff_Models)
summary(LM_Abd_T)

plot(LM_Data_Abd$Abs_Latitude~LM_Data_Abd$Diff_Models)


# Revenue LM

LM_Data_Rev <- Results_Data %>% 
  mutate(Abs_Latitude = abs(Latitude)) %>% 
  filter(
    Data_Type == "Revenue",
    Measure == "Mean",
    Touching_b == "Surrounding",
    time_period == "Mid Century",
    RCP == 85,
    Diff_Models != 0)

LM_Rev  <- lm(LM_Data_Rev$Abs_Latitude~LM_Data_Rev$Diff_Models)
summary(LM_Rev)

plot(LM_Data_Rev$Abs_Latitude~LM_Data_Rev$Diff_Models)


# Abundance LM Oppen

LM_Data_Open <- Results_Data %>% 
  mutate(Abs_Latitude = abs(Latitude)) %>% 
  filter(
    Data_Type == "Biomass",
    Measure == "Mean",
    Touching_b == "Unprotected",
    time_period == "Mid Century",
    RCP == 85,
    Diff_Models != 0)

LM_One_Open  <- lm(LM_Data_Open$Abs_Latitude~LM_Data_Open$Diff_Models)
summary(LM_One_Open)

plot(LM_Data_Open$Abs_Latitude~LM_Data_Open$Diff_Models)


# Da fuuuuuuuck is wrong with those 0's

LM_Data <- Results_Data %>% 
  mutate(Abs_Latitude = abs(Latitude)) %>% 
  filter(
    Data_Type == "Biomass",
    Measure == "Mean",
    # Touching_b == "MPA",
    time_period == "Mid Century",
    RCP == 85,
    Diff_Models == 0)

```

## 6.6 Mean and SD stats 

Averages and s.d. for the results section

```{r stats_mean_change, eval = F, echo = F}

#tropical MPAs vs Polar 
Region_dat <- Delta_Time %>% 
  filter(Model == "MPA") %>% 
  mutate(
    Geo_Region = ifelse(Latitude >= 66.5, "Polar_N", # If MPA and Fish are cero, then no change
                        ifelse(Latitude >= 23.5 & Latitude < 66.5, "Sub_Trop_N", # If MPA is cero but Fish >0 then -100 
                               ifelse(Latitude >= -23.5 & Latitude < 23.5, "Tropical", # If MPA > 0 but Fish = 0, then +100
                                      ifelse(Latitude <= -23.5 & Latitude > -66.5, "Sub_Trop_S", # If MPA is cero but Fish >0 then -100 
                                             "Polar_S")
                               )
                        )
    )
  )


Non_tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region!="Tropical", time_period == "Mid Century", RCP==85)

mean(Non_tropicalMPA_dat$MCP_Chng)
sd(Non_tropicalMPA_dat$MCP_Chng)

Non_tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region!="Tropical", time_period == "End of Century", RCP==85)

mean(Non_tropicalMPA_dat$MCP_Chng)
sd(Non_tropicalMPA_dat$MCP_Chng)

#tropical 
tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region=="Tropical", time_period == "Mid Century", RCP==85)

mean(tropicalMPA_dat$MCP_Chng)
sd(tropicalMPA_dat$MCP_Chng)

tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region=="Tropical", time_period == "End of Century", RCP==85)

mean(tropicalMPA_dat$MCP_Chng)
sd(tropicalMPA_dat$MCP_Chng)

#high vs low RCP
tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region=="Tropical", time_period == "End of Century", RCP==26)

mean(tropicalMPA_dat$MCP_Chng)
sd(tropicalMPA_dat$MCP_Chng)

Non_tropicalMPA_dat = Region_dat%>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1, Geo_Region!="Tropical", time_period == "End of Century", RCP==26)

mean(Non_tropicalMPA_dat$MCP_Chng)
sd(Non_tropicalMPA_dat$MCP_Chng)

# head(Delta_Time)
# max(Delta_Time$Per)
# min(Delta_Time$Per)


#min and max change in biomass 
data <- Delta_Time %>% filter(Model == "MPA", Data_Type == "Abd",  Touching == 1 | Touching == 2)

mean(data$MCP_Chng)
sd(data$MCP_Chng)
max(data$MCP_Chng)
min(data$MCP_Chng)


touchingpositivedata = Delta_Time %>% filter (Model == "MPA", Data_Type == "Abd", Per > 0, Touching == 2, RCP == 85, time_period == "End of Century")

MPApositivedata = Delta_Time %>% filter(Model == "MPA", Data_Type == "Abd", Per > 0, Touching == 1, RCP == 85, time_period == "End of Century")

Openpositivedata = Delta_Time %>% filter(Model == "MPA", Data_Type == "Abd", Per > 0, Touching == 0 & RCP == 85, time_period == "End of Century")

mean(touchingpositivedata$MCP_Chng)
sd(touchingpositivedata$MCP_Chng)

mean(MPApositivedata$MCP_Chng)
sd(MPApositivedata$MCP_Chng)

mean(Openpositivedata$MCP_Chng)
sd(Openpositivedata$MCP_Chng)

#touching vs MPA total 
touchingpositivedata = Delta_Time %>% filter (Model == "MPA", Data_Type == "Abd", Touching == 2, RCP == 85, time_period == "End of Century")

MPApositivedata = Delta_Time %>% filter(Model == "MPA", Data_Type == "Abd", Touching == 1, RCP == 85, time_period == "End of Century")

Openpositivedata = Delta_Time %>% filter(Model == "MPA", Data_Type == "Abd", Touching == 0 & RCP == 85, time_period == "End of Century")

mean(touchingpositivedata$MCP_Chng)
sd(touchingpositivedata$MCP_Chng)

mean(MPApositivedata$MCP_Chng)
sd(MPApositivedata$MCP_Chng)

mean(Openpositivedata$MCP_Chng)
sd(Openpositivedata$MCP_Chng)

#comparing models

sumy_models <- Results_Data %>% 
  group_by(time_period, Data_Type, RCP, Touching) %>%
  summarize(MEAN_fish=mean(Fish), SD_fish=sd(Fish), Mean_MPA = mean(MPA), SD_MPA = sd(MPA))

```

# 7 Sensitivity Analysis

We need to test the sensitivity of the larvae fix parameters of the DBEM. There are three main components:

- *DiffCoef*, which talks about each species diffusion rate, 
- *LarSurv* = 0.15, determines the larval survival,
- *rLarSettle* = 0.15, determines the larval settlement rate

We will run the DBEM in compu-Canada 4 times (2 increasing and 2 decreasing) for each variable and model (Fish and MPA), for a total of 40 random species using the GFDL85 from 1995 to 2014 (today) as follows:

- *DiffCoef*, -0.10; -0.20; +0.10; +0.20
- *LarSurv* = 0.15, 0.5; 0.10; 0.20; 0.25
- *rLarSettle* = 0.15, 0.5; 0.10; 0.20; 0.25

At the end we can produce histograms and to see if there are differences between variables.

## 7.1 Choosing the species

```{r Choose_Species, eval = F, echo = F}

# Functions needed to get species

source(here::here("DBEM/Functions_Paper2/Get_Spp_Grid.r")) # Chagos grid for species there
source("./DBEM/Functions/DBEM_imp_F.r") # Imports a single species

# Data needed to get species
Chagos_Grid <- fread("/nfs/mpasandclimatechange-data/Data/MPA/grid_MPA_touching.csv",header = TRUE) %>%
  filter(NAME == "British Indian Ocean Territory Marine Protected Area (Chagos)") %>% 
  rename(INDEX = Seq) %>% 
  select(INDEX, NAME)

# Get taxon list from what we've modeled so far
Taxon_List <- inner_join(mpa_model_species, fish_model_species) %>% pull(x)

# Get species list for sensitivity analysis using the GFDL 26

# Global Variables
RCP = "26"
Model <- "Fish"
Initial_Y = 1995
Final_Y = 2014
GCM = "GFDL26"
# Run function Get_Spp_Grid
sensitivity_spp <- bind_rows(lapply(Taxon_List, FUN=Get_Spp_Grid, Chagos_Grid))


selected_sensitivity_spp <- slice(sensitivity_spp, sample(1:40)) %>% 
  select(TaxonKey)

readr::write_csv(selected_sensitivity_spp,
          "RunSppListSen10.txt")
sample(c(0,1), 100, replace = TRUE)

# Send RunSppListSen10.txt to computeCanada over terminal

```

## 7.2 Sensitivity Results

```{r Sens_Results, eval = F, echo = F}

# Load Data need
MPA_Grid <- fread("/nfs/mpasandclimatechange-data/Data/MPA/grid_MPA_touching.csv",header = TRUE) %>% 
  # filter(NAME == "British Indian Ocean Territory Marine Protected Area (Chagos)") %>% 
  rename(INDEX = Seq) %>% 
  select(INDEX, NAME,Touching)

# Load Sensitivity analysis data
Fish_Sen <- fread("/nfs/mpasandclimatechange-data/Data/Results/Sensitivity/Sensitivity_Fish.csv")

mean(Fish_Sen$total)
max(Fish_Sen$total)


MPA_Sen <- fread("/nfs/mpasandclimatechange-data/Data/Results/Sensitivity/Sensitivity_MPA.csv")

max(MPA_Sen$total)
mean(MPA_Sen$total)


# Estimate the percentage change

Sens_PerChange <- Sen_Data %>% 
  filter(
    Data_Type %in% c("Abd"),
    Measure == "Mean"
  ) %>% 
  select(-n) %>% 
  spread("Model","total") %>% 
  mutate(
    MPA = ifelse(is.na(MPA), 0, MPA), # I believe there are parts that MPA model does not have?
    Fish = ifelse(is.na(Fish), 0, Fish),
    Diff_Models = ifelse(MPA == 0 & Fish == 0, 0, # If MPA and Fish are cero, then no change
                         ifelse(MPA == 0 & Fish > 0, -100, # If MPA is cero but Fish >0 then -100 
                                ifelse(MPA > 0 & Fish == 0, 100, # If MPA > 0 but Fish = 0, then +100
                                       ((MPA-Fish)/((MPA+Fish)/2))*100
                                )
                         )
    ),
    # Just to set the percentage bounds
    Per = ifelse(Diff_Models <= -25, -25,
                 ifelse(Diff_Models >= 25, 25,Diff_Models)
    ),
    # For plot labels
    # Data_Type = ifelse(Data_Type == "Abd","Biomass","Revenue")
  ) %>% 
  left_join(MPA_Grid,
            by = "INDEX") %>% 
  mutate(
    Touching_b = ifelse(Touching == 0,"Unprotected",
                        ifelse(Touching == 1, "MPA",
                               ifelse(Touching == 2, "Surrounding",
                                      NA
                               )
                        )
    )
  )





max(Sens_PerChange$Diff_Models)
min(Sens_PerChange$Diff_Models)
```

## 7.3 Sensitivity Figures

```{r Sens_Figures, eval = F, echo = F}

Sens_PerChange %>% 
  filter(Touching == 2 & Per > 0 & Per < 25) %>% 
  ungroup() %>% 
  mutate(
    Sen =  ifelse(Sen == "Sur","Survival",
                  ifelse(Sen == "Set","Settlement","Diffusion")
                  )
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(
      x = Per
    ),
    bins = 100
  ) +
  facet_wrap(~Sen+Coef,
             scales = "free") +
  labs(x = "Differences between models (%)",
       y = "Frequency") +
  ggtheme_Plot()

 ggsave(
    plot = last_plot(),
    width = 14,
    height = 10,
    units = "in",
    # filename = "larvae_sensitivity.png",
    # path=  "./data/Data/Results/Sensitivity"
    # Info for final plots 
    filename ="Figure4.png",
    path = "/nfs/mpasandclimatechange-data/Global Paper/Submission_NCC/Figures/"
  )


```

# 8. Supplemental material

## Fig S1.Delta time for all

Fig S1. Change in biomass under climate change, incorporating current no-take MPAs.** Results for mid (2041-2060) and end (2081-2099) century in reference to present (1995-2014) under a low (RCP 2.6) and high emission scenario (RCP 8.5). Results from the MPA model with MPAs included in this study outlined in black.


```{r Fig_sone_plot, eval = T, echo = F}

# Do not subset RCP nor timeframe 

ggplot() +
  geom_tile(data = subset(Delta_Time, Model == "MPA" & Data_Type == "Abd" ),
            aes(
              x = Longitude,
              y = Latitude,
              fill = Per
            )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  geom_sf(data = MPA_sf, colour = "black", fill = NA, size = 0.5) +
  scale_fill_gradient2("Percentage Change in Biomass (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
  ) +
  ggtheme_Map() +
  guides(fill = guide_legend(title.position = "top",
                             label.position = "bottom",
                             title.hjust = 0.5,
                             nrow = 1,
                             byrow = TRUE)
  ) +
  facet_wrap(~time_period + RCP,
             ncol= 2) +
  ggsave(
    width = 12,
    height = 7,
    units = "in",
    filename = "FigureS1.png",
    path= "./data/Global Paper/Submission/Figures"
  )

```

## Fig S2 - Supplemental

This is the same figure as Figure 2. But for the end of the century

```{r Fig_S2_Supplemental, eval = T, echo = F}

# --------------------- #
# Create maps (A and B)
# --------------------- #

# Abundance Map
Map_Abd <- ggplot() +
  geom_raster(data = subset(Results_Data, Data_Type == "Biomass" & time_period == "End of Century"),
              aes(
                x = Longitude,
                y = Latitude,
                fill = Per
              )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  scale_fill_gradient2("Change relative to present (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
                       ) +
  ggtheme_Map() +
  theme(legend.position = "")
  

# Revenue Map
Map_Rev <- ggplot() +
  geom_tile(data = subset(Results_Data, Data_Type == "Revenue" & time_period == "End of Century"),
              aes(
                x = Longitude,
                y = Latitude,
                fill = Per
              )
  ) +
  geom_sf(data = World_Land_sf, colour = "grey50", fill = "grey50") +
  geom_sf(data = MPA_sf, colour = "grey50", fill = "grey50", size = 0.5) +
  scale_fill_gradient2("Differences between models (%)",
                       labels = c("<-25",seq(-20,20,5),">25"),
                       breaks = c(seq(-25,25,5)),
                       na.value = "grey90"
                       ) +
  ggtheme_Map() +
  guides(fill = guide_legend(title.position = "top",
                             label.position = "bottom",
                             title.hjust = 0.5,
                             nrow = 1,
                             byrow = TRUE)
  )

# Get legend for cowplot
legend_map <- get_legend(Map_Rev)

# Re-plot without legend
Map_Rev <- Map_Rev +
  theme(legend.position = "")

# --------------------- #
# Create histograms (C)
# --------------------- #

# Abundance Histogram (No Latitudinal differentiation)

Hist_Abd <- ggplot() + 
  geom_path(data = subset(Spillover_diff_Lat, Data_Type == "Biomass" & time_period == "End of Century"), 
            aes(y=Latitude, 
                x=total_value, 
                color=Touching_b),
            size = 1) +
  geom_path(data = subset(Spillover_diff_Lat_1, Data_Type == "Biomass" & time_period == "End of Century"),
            aes(y=Latitude, 
                x=total_value, 
                color = "Total"),
            size = 1
            ) +
  scale_color_manual(values = wes_palette("Darjeeling2")) +
  scale_x_continuous(breaks = 0) +
  # scale_color_manual(values=c("dodgerblue3", "firebrick3", "black", "seagreen3"))+
  ggtheme_Plot() +
  labs(x = "",
       y = "") +
  theme(
  axis.text.y = element_blank(),
  legend.position = "",
  legend.key.width = unit(2,"line"),
  legend.title = element_text(size = 22),
  legend.text = element_text(size = 20)
  ) +
  geom_vline(xintercept = 0, colour = "black", linetype = "dotted") 


Hist_Rev <- ggplot() + 
  geom_path(data = subset(Spillover_diff_Lat, Data_Type == "Revenue" & time_period == "End of Century"), 
            aes(y=Latitude, 
                x=total_value, 
                color=Touching_b),
            size = 1)  +
  geom_path(data = subset(Spillover_diff_Lat_1, Data_Type == "Revenue" & time_period == "End of Century"),
            aes(y=Latitude, 
                x=total_value, 
                color = "Total"), 
            # linetype = "dotted",
            size = 1) +
  geom_vline(xintercept = 0, colour = "black",linetype = "dotted") +
  scale_color_manual("Spillover effect by latitude",
                     values = wes_palette("Darjeeling2")
  ) +
  scale_x_continuous(breaks = 0) +
  # scale_color_manual(values=c("dodgerblue3",
  #                             "firebrick3",
  #                             "black",
  # "seagreen3"))+
  ggtheme_Plot() +
  labs(x = "",
       y = "") +
  theme(
    axis.text.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_text(size = 22),
    legend.text = element_text(size = 20)
  ) +
  guides(color = guide_legend(title.position = "top",
                              label.position = "right",
                              title.hjust = 0.5,
                              nrow = 1,
                              byrow = TRUE)
  )

# Get legend for cowplot
legend_hist <- get_legend(Hist_Rev)

# Re-plot without legend
Hist_Rev <- Hist_Rev +
  theme(legend.position = "")

# --------------------- #
# Plot them all
# --------------------- #

plot <- ggdraw() +
  # Abundance
  draw_plot(Map_Abd, x = 0, y = 0.6, width = 0.6, height = 0.4) +
  draw_plot(Hist_Abd, x = 0.59, y = 0.59, width = 0.3, height = 0.4) +
  # Revenue
  draw_plot(Map_Rev, x = 0, y = 0.2, width = 0.6, height = 0.4) +
  draw_plot(Hist_Rev, x = 0.57, y = 0.19, width = 0.3, height = 0.4) +
  # Legends
  draw_plot(legend_map, x = 0, y = 0.1, width = 0.59, height = 0.1) +
  draw_plot(legend_hist, x = 0.60, y = 0.1, width = 0.3, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("A", "B", "C"), 
                  size = 30,
                  x = c(0.0, 0.0, 0.56), 
                  y = c(1, 0.6, 1)
  ) +
  # Uncomment for latitudinal version 
  draw_plot_label(label = c("Revenue", "Abundance"),
                  size = 40,
                  x = c(0.91, 0.91),
                  y = c(0.50, 1),
                  angle = 270,
                  colour = "black"
  )

# Path and name for submission
# Save plot 
save_plot("./data/Global Paper/Submission/Figures/FigureS2.png",
          plot,
          base_height = 15,
          base_width = 20)

```
